

%%% Choose a language %%%

\newif\ifEN
% \ENtrue   % uncomment this for english
\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
%\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
%\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Optimalizace rozmístění stanic pro nabíjení elektrických vozidel}
\def\ThesisAuthor{David Beinhauer}
\def\YearSubmitted{2022}

% department assigned to the thesis
\def\Department{Katedra teoretické informatiky a matematické logiky}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Katedra}

\def\Supervisor{Mgr. Martin Pilát, Ph.D.}
\def\SupervisorsDepartment{Katedra teoretické informatiky a matematické logiky}

% Study programme and specialization
\def\StudyProgramme{Informatika}
\def\StudyBranch{Informatika se specializací Umělá inteligence}

\def\Dedication{%
Rád bych poděkoval panu Mgr. Martinu Pilátovi, Ph.D. za odborné vedení
mé práce, cenné rady a vstřícnost při konzultacích a vypracování bakalářské práce. 
Dále bych rád poděkoval členům své rodiny a přátelům za podporu během psaní
bakalářské práce.
}

\def\AbstractEN{As the number of electric vehicles grows, so does the need to create a suitable
network of charging stations. A solution of this problem can be significantly
improved by the usage of suitable optimization techniques.
We implement a simplified traffic simulator serving as a suitable tool for 
their analysis.
We also analyze optimization techniques using the so-called greedy algorithm,
genetic algorithm and k-means algorithm. Based on the experiments, the optimizations 
using the genetic algorithm and the greedy algorithm showed noticeably better results.
The k-means method did not show signs of results better than a
random approach.
}

\def\AbstractCS{S rostoucím počtem elektrických vozidel roste i potřeba vytvořit vhodnou 
infrastrukturu pro jejich nabíjení. K řešení tohoto problému může výrazně 
napomoci použití vhodných optimalizačních metod. V práci jsme implementovali 
zjednodušený simulátor dopravy sloužící jako vhodný nástroj pro jejich analýzu.
Analyzovali jsme také optimalizační metody tzv. hladovým algoritmem, 
genetickým algoritmem a algoritmem k-means. Na základě experimentů 
vykazovala prokazatelně lepší výsledky optimalizace za využití 
genetického algoritmu a hladová optimalizace. K-means optimalizace 
nevykazovala známky lepších výsledků oproti náhodnému přístupu.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{{optimalizace}, {simulátor dopravy}, {k-means}, {genetický algoritmus}
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{Optimization of the Placement of Electric Vehicle Charging Stations}
\def\DepartmentEN{Department of Theoretical Computer Science and Mathematical Logic}
\def\DeptTypeEN{Department}
\def\SupervisorsDepartmentEN{Department of Theoretical Computer Science and Mathematical Logic}
\def\StudyProgrammeEN{Computer Science}
\def\StudyBranchEN{Computer Science with specialisation in Artificial Intelligence}
\def\KeywordsEN{{optimization}, {traffic simulator}, {k-means}, {genetic algorithm}}
\fi
